The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-16 paper.tex
update

\begin{abstract}
\end{abstract}

@@

 The fiducial run (leftmost column) with the initial condition specified in Section \ref{Methodology}\
 shows that the edge of the outermost bubbles is indeed a forward shock,\
 expanding 12.5 kpc above and below the Galactic plane,\
 and with a radius of about 6.8 kpc along the plane.\
 We note that the overall extent of the outermost bubbles is comparable to\
 the two spherical objects of a radius 6-7 kpc proposed by \citet{Predehl2020} for modeling the eROSITA bubbles.

 The left column of \Cref{fig__profile} shows the profiles cut at\
 the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.\
 The temperature profile in the left column indicates that\
 most of the region between the forward shock and the turbulent region\
 is around 0.3-0.4 keV \citep{Miller2016,Kataoka2018}.

 Followed by the forward shock is a turbulent and high temperature ($\sim2$ keV) plasma.\
 By observing X-ray absorption lines through the hot\
 gaseous halo along many different sight lines in the sky, Miller& Bregman (2012)\
 found that the ratio between O viii and O vii\
 column densities is enhanced for sight lines that pass through\
 the Fermi bubbles, indicating gas temperature of a few times keV\
 inside the bubbles.

>>>>

\begin{abstract}
% out of the Galactic center on either side of the Galactic disk
\end{abstract}

@@

 The fiducial run (leftmost column) with the initial condition specified in Section \ref{Methodology}\
 shows that the edge of the outermost bubbles is indeed a forward shock,\
 expanding 12.5 kpc above and below the Galactic plane,\
 and with a semiminor axis about 6.8 kpc on the plane.\
 We note that the overall extent of the outermost bubbles is comparable to\
 the two spherical objects of a radius 6-7 kpc proposed by \citet{Predehl2020} for modeling the eROSITA bubbles\
 based on X-ray emissions.

 The left column of \Cref{fig__profile} shows the profiles cut at\
 the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.\
 The temperature profile in the left column indicates that\
 most of the region between the forward shock and the turbulent zone\
 is around 0.3-0.4 keV, similar to that observed by \citet{Miller2016} and \citet{Kataoka2018}.

 Followed by the forward shock is a turbulent and hot plasma.\
 The full extent of the hot plasma is approximately agree with the observation \citep{Su2010}.
 Moreover, the temperature of the plasma is high as 2 keV, comparable to that of the \textit{Fermi} bubbles\
 by observing X-ray absorption lines through the hot\
 gaseous halo along many different sight lines in the sky \citep{Miller_2013}.\

 % which we will interpret as the \textit{Fermi} bubbles.\
